Understanding Suicide Rates: Exploring Gender and Age Patterns That Lead to Various Risk Factors Associated with Suicidal Behaviour

### 2024-04-02 paper/paper.qmd
update paper/paper.qmd

---
title: "Understanding Suicide Rates: Exploring Gender and Age Patterns That Lead to Various Risk Factors Associated with Suicidal Behaviour"
subtitle: "My subtitle if needed"
author: 
  - Sarah Lee
thanks: "Code and data are available at: https://github.com/sarahhhh02/final-paper.git"
date: today
date-format: long
abstract: "This paper utilizes data from Statistics Canada, retrieving data related to the Suicide Rates. Analysing the relationship with gender, it is shown that suicide rates tend to be higher in male rather than female. However, suicide rates vary between gender through age, as we find that adolecent females may have a higher rate for suicidal attempts. The results of these findings aids policymakers, public health officials, and mental health professionals to develop a more effective and strategic suicide prevention tailored for the population."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Understanding Suicide Rates: Exploring Gender and Age Patterns That Lead to Various Risk Factors Associated with Suicidal Behaviour"
author: 
  - Sarah Lee
thanks: "Code and data are available at: https://github.com/sarahhhh02/final-paper.git"
date: today
date-format: long
abstract: "This paper utilizes data from Statistics Canada, retrieving data related to the Suicide Rates. Analysing the relationship with gender, it is shown that suicide rates tend to be higher in male rather than female. However, suicide rates vary between gender through age, as we find that adolecent females may have a higher rate for suicidal attempts. The results of these findings aids policymakers, public health officials, and mental health professionals to develop a more effective and strategic suicide prevention tailored for the population."
format: pdf
number-sections: true
bibliography: references.bib
---
